Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-07 paper.tex
review Program Synthesis via Counter-Example Guided Inductive Synthesis (CEGIS)

The input specification provided to the program synthesizer is of the form $\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. The ground terms is interpreted over some finite domain $\mathcal{D}$. The {\sc Synthesize} and {\sc Verify} phases interact via a finite set of test vectors {\sc inputs} that is updated incrementally. Given the aforementioned specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{P}$ satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness is a candidate solution to the full synthesis formula, which is passed to the {\sc verify} phase to check whether it is a full solution ({\it i.e.}, $\vec{P}$ satisfies the specification $\sigma(\vec{x}, \vec{P})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the {\sc synthesize} phase in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. It is worth noting that each iteration of the loop adds a new input to the finite set $\text{\sc inputs}$ that is used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate a finite number of times.
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.12]{figure4.eps}
	\caption{Counter-Example Guided Inductive Synthesis.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

>>>>

The correctness specification $\sigma$ provided to the program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$ where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers. The ground terms is interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can encoded using the SMT solvers bit-vectors theory. The {\sc Synthesize} and {\sc Verify} phases interact via a finite set of test vectors {\sc inputs} that is updated incrementally. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, this witness is a candidate solution to the full synthesis formula, which is passed to the {\sc verify} phase to check whether it is a full solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the {\sc synthesize} phase in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.12]{figure4.eps}
	\caption{Counter-Example Guided Inductive Synthesis.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

Note that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$ that is used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate a finite number of times. However, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$. In order to avoid exploring all possible values, machine learning techniques can be used in the {\sc Synthesize} phase to learn from experience, {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}.
